Modelling Federal Open Market Committee Decisions Using ML and NLP

### 2019-05-04 presentation/paper.tex
update

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{Topic-Model-3-topics.PNG}
  \caption{Top 15 Words Distributed Over Three Latent Topics}
  \label{fig:LDA}
\end{figure}

@@

L1 regularization has the effect of forcing feature selection, and as we observe the Logistic Lasso model performs best Tri-grams to 7-grams and performance significantly drops with larger Ngrams.  \vertSpace

@@

% Bibliography
%-----------------------------------------------------------------
\begin{thebibliography}{99}

>>>>

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
  \caption{Top 15 Words Distributed Over Three Latent Topics}
  \label{fig:LDA}
\end{figure}

@@

L1 regularization has the effect of forcing feature selection, and as we observe the Logistic Lasso model performs best with Tri-grams to 7-grams while the F1 measure significantly drops with larger Ngrams.  \vertSpace

@@

\subsection{Neural Network} 
% Bibliography
%-----------------------------------------------------------------
\begin{thebibliography}{99}

### 2019-05-04 presentation/presentation.tex
update

\frametitle{Introduction}
test intro
\end{frame}

\frametitle{Introduction}
test 2

@@

\begin{frame}
\frametitle{Data}
TEST
\end{frame}

\begin{frame}
\frametitle{Summary}

\begin{itemize}
  \item The \alert{first main message} of your talk in one or two lines.
\end{itemize}
\end{frame}

>>>>

\begin{figure}[h!]
\includegraphics[width=1\textwidth]{../output/data_for_graphs/Topic-Model-3-topics.PNG}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/log_lasso_f1".pdf}
\includegraphics[width=.3\textwidth]{"../output/data_for_graphs/naive_bayes_f1".pdf}
\end{center}
\end{figure}

@@
